Statistical Searches for Microlensing Events in Large, Non-Uniformly Sampled Time-Domain Surveys: A Test Using Palomar Transient Factory Data

### 2013-10-31 text/paper/ms.tex

\section{Searching for events in the full PTF dataset}\label{sec:search}
To identify candidate microlensing events in the $1.1\times10^9$ light curves with $>$10 $R$-band observations, we:
%We apply the 1\% FPR cut to the 2097 PTF fields ($\sim$15,224 deg$^2$) with $>$10 $R$-band observations using the variability index $\eta$. Our procedure is as follows:
\begin{enumerate}
	\item select a field from the 2097 fields with $>$10 good $R$-band observations and run Monte Carlo simulations to compute the 1\% FPR limiting values for $\eta$, $\Delta \chi^2$, and $J$ for that field;
	\item compute $\eta$ for all the light curves in the field. While $\sim$10\% of the light curves pass the quality cut described in Section~\ref{sec:detection_eff}, only $\sim$0.1-0.5\% of these pass the FPR cut determined from the Monte Carlo simulations;
	\item for fields with SDSS coverage, we use Data Release 9 photometry \citep{dr9paper} to remove sources typed as Galaxy or QSO (using \texttt{objc\_type}\footnote{{\tt http://www.sdss3.org/dr9/algorithms/classify.php}}) and flag candidate quasars \citep[using the cuts described in][]{richards02}; this eliminates $\sim$90\% of the remaining light curves;
	\item fit a microlensing event model and subtract the model, then recompute $\eta$ for all the selected light curves;
	\item reject the light curves for which the new value of $\eta$ still passes the cut\footnote{These are probably periodic variables.} --- this step eliminates $\sim$90-95\% of the remaining light curves;
	\item retain any surviving light curves for further inspection. Typically, there is $\lapprox$1 such light curve per field.
\end{enumerate}
% Turn this into a table, with number of objects left over after each cut?

>>>>

\section{Searching for events in the full PTF dataset}\label{sec:search}
To identify candidate microlensing events we: %in the $1.1\times10^9$ light curves with $>$10 $R$-band observations, we:
%We apply the 1\% FPR cut to the 2097 PTF fields ($\sim$15,224 deg$^2$) with $>$10 $R$-band observations using the variability index $\eta$. Our procedure is as follows:
\begin{enumerate}
	\item select the light curves from one of the 2097 fields with $>$10 $R$-band observations;
	\item identify those light curves with more than 50\% good data points and $>$10 good observations (see Section~\ref{sec:detection_eff}) and run Monte Carlo simulations to compute the 1\% FPR limiting values for $\eta$, $\Delta \chi^2$, and $J$ for that field;
	\item compute $\eta$ for all the light curves in the field. While $\sim$10\% of the light curves pass the quality cut described above, only $\sim$0.1-0.5\% of these survive the FPR cut determined from the Monte Carlo simulations;
	\item for fields with SDSS coverage, we use Data Release 9 photometry \citep{dr9paper} to remove sources typed as Galaxy or QSO (using \texttt{objc\_type}\footnote{{\tt http://www.sdss3.org/dr9/algorithms/classify.php}}) and flag candidate quasars \citep[using the cuts described in][]{richards02}; this eliminates $\sim$90\% of the remaining light curves;
	\item fit a microlensing event model and subtract the model, then recompute $\eta$ for all the selected light curves;
	\item reject the light curves for which the new value of $\eta$ still passes the cut\footnote{These are probably periodic variables.} --- this step eliminates $\sim$90-95\% of the remaining light curves;
	\item retain any surviving light curves for further inspection. Typically, there is $\lapprox$1 such light curve per field.
\end{enumerate}
% Turn this into a table, with number of objects left over after each cut?
